Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits

### 2022-11-21 04_paper/isq_manuscript.Rmd
hot off the press

---
title: "Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::pdf_document2: 
    toc: false
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{indentfirst}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

abstract: "Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts? We bring a novel perspective to this issue by considering its international recognition efforts through public diplomacy and news. Chinese. We propose that Beijing’s foreign policy tools, *Xinhua* media coverage of developing countries and bilateral diplomatic activities, are associated with its overseas financing allocation decisions. We expect greater media coverage and bilateral diplomatic activity of a developing country to correlate with more foreign aid giving, but not so much with its debt. It is generally believed that foreign aid is motivated by a country’s developmental needs, hence perceived to be conducive to constructing a positive image of being a donor than lending interest-based debts. To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of *Xinhua* news articles in the Cline Center for Advanced Social Research. We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors. Aid-recipient countries disproportionately get more media coverage on the state of their economy and developmental needs. Meanwhile, China is more likely to provide loans to diplomatically aligned countries. Our results dispel the myths that China is a “rouge donor” or a designer of “debt-trap diplomacy.” Instead, we provide suggestive evidence that, much like traditional donors, China’s foreign aid and debt allocations present a versatile foreign policy tool in international politics."
---

>>>>

---
#title: "Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
#author: ["Lucie Lu","Miles D. Williams"]
#date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::pdf_document2: 
    toc: false
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{indentfirst}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

#abstract: "Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts? We bring a novel perspective to this issue by considering its international recognition efforts through public diplomacy and news. Chinese. We propose that Beijing’s foreign policy tools, *Xinhua* media coverage of developing countries and bilateral diplomatic activities, are associated with its overseas financing allocation decisions. We expect greater media coverage and bilateral diplomatic activity of a developing country to correlate with more foreign aid giving, but not so much with its debt. It is generally believed that foreign aid is motivated by a country’s developmental needs, hence perceived to be conducive to constructing a positive image of being a donor than lending interest-based debts. To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of *Xinhua* news articles in the Cline Center for Advanced Social Research. We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors. Aid-recipient countries disproportionately get more media coverage on the state of their economy and developmental needs. Meanwhile, China is more likely to provide loans to diplomatically aligned countries. Our results dispel the myths that China is a “rouge donor” or a designer of “debt-trap diplomacy.” Instead, we provide suggestive evidence that, much like traditional donors, China’s foreign aid and debt allocations present a versatile foreign policy tool in international politics."
---
